Predicting sales of newly published books

### 2015-10-31 paper.tex
results obtained using the dataset with features selected using SOM
adding details about the features selected using the SOM

\textbf{ TODO: add the SOM analysis }

@@

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with 7 variables per book (obtained 
using the SOM analysis) can be shown in Table \ref{tabla:resultsSOM}.
%In this dataset, every book is described using numerical variables, and thus, 
%processing the data to build the different models is a fast task.
%***************************************
% TODO: falta rellenar la tabla, una vez que hagamos el análisis con el SOM y decidamos qué variables incluir en este dataset
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
\hline
  M5P     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  LR      & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  SVM     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  kNN     & x $\pm$ y     & x  & x  & x    & x  \\
\hline
  MLP     & x $\pm$ y   & x $\pm$ y & x $\pm$ y  & x $\pm$ y  & x $\pm$ y   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset obtained after the SOM analysis.}}
\label{tabla:resultsSOM}
\end{table*}

@@

\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
\hline
  M5P     & 2.27 $\pm$ 0.02     & 195.97  & 629.33  & 34.94    & 45.62  \\
\hline
  LR      & 0.38 $\pm$ 0.01     & 256.19  & 549.19  & 45.68    & 39.81   \\
\hline
  SVM     & 132.64 $\pm$ 2.86   & 230.66  & 613.27  & 41.12    & 44.45   \\
\hline
  kNN     & 0.06 $\pm$ 0.01     & 214.76  & 551.33  & 38.29    & 39.96   \\
\hline
  MLP     & 130.77 $\pm$ 1.51   & 326.60 $\pm$ 75.77 & 687.61 $\pm$ 55.70  & 58.23 $\pm$ 13.51  & 49.84 $\pm$ 4.04   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 9 variables per book.}}
\label{tabla:results9}
\end{table*}

@@

\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  M5P     & 2.02 $\pm$ 0.01     & 205.52  & 556.90  & 36.64     & 40.37  \\
\hline
  LR      & 0.32 $\pm$ 0.00     & 261.04  & 547.42  & 46.54     & 39.68   \\
\hline
  SVM     & 81.74 $\pm$ 1.66    & 242.26  & 606.07   & 43.19    & 43.93   \\
\hline
  kNN     & 0.05 $\pm$ 0.00     & 216.05  & 506.34  & 38.52    & 36.70   \\
\hline
  MLP     & 47.80 $\pm$ 0.51    & 318.29 $\pm$ 43.96 & 587.50 $\pm$ 51.50  & 56.75 $\pm$ 7.84  & 42.59 $\pm$ 3.73   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 4 variables per book.}}
\label{tabla:results4}
\end{table*}

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=fig_time.eps,width=11cm}
\caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 9, 4 and X features each one). Plot shows that using categorical variables as part of the dataset makes the problem hard to solve. As expected, simpler methods are much faster to build the model than the complex ones.}}
\label{fig:time}
\end{center}
\end{figure}

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=fig_rae.eps,width=11cm}
\caption{\small{Relative absolute error (RAE $\%$) obtained after applying the five methods to the reduced datasets (16, 9, 4 and X features each one). The M5P model obtains the lowest errors, whatever the dataset used.}}
\label{fig:rae}
\end{center}
\end{figure}

>>>>

After the SOM analysis, the following variables have been selected: 
\emph{retail pricer, reprints, number of reprints, gifts, units distributed as novelty, print-run, total sales }.

@@

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with 7 variables per book (obtained 
using the SOM analysis) can be shown in Table \ref{tabla:resultsSOM}.
%In this dataset, every book is described using numerical variables, and thus, 
%processing the data to build the different models is a fast task.
%***************************************
% TODO: falta rellenar la tabla, una vez que hagamos el análisis con el SOM y decidamos qué variables incluir en este dataset
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
\hline
  M5P     & 1.74 $\pm$ 0.10     & 218.81  & 661.85  & 39.01    & 47.98  \\
\hline
  LR      & 0.27 $\pm$ 0.02     & 258.82  & 582.74  & 46.15    & 42.24  \\
\hline
  SVM     & 45.58 $\pm$ 1.89    & 240.18  & 614.30  & 42.82    & 44.53  \\
\hline
  kNN     & 0.04 $\pm$ 0.00     & 221.21  & 520.17  & 39.44    & 37.71  \\
\hline
  MLP     & 8.99 $\pm$ 0.10   & 353.70 $\pm$ 57.74 & 624.87 $\pm$ 86.77  & 63.06 $\pm$ 10.29  & 45.30 $\pm$ 6.29   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset obtained after the SOM analysis (7 variables per book).}}
\label{tabla:resultsSOM}
\end{table*}

@@

\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%) & RRSE (\%)      \\
\hline
  M5P     & 2.27 $\pm$ 0.02     & 195.97  & 629.33  & 34.94    & 45.62  \\
\hline
  LR      & 0.38 $\pm$ 0.01     & 256.19  & 549.19  & 45.68    & 39.81   \\
\hline
  SVM     & 132.64 $\pm$ 2.86   & 230.66  & 613.27  & 41.12    & 44.45   \\
\hline
  kNN     & 0.06 $\pm$ 0.01     & 214.76  & 551.33  & 38.29    & 39.96   \\
\hline
  MLP     & 130.77 $\pm$ 1.51   & 326.60 $\pm$ 75.77 & 687.61 $\pm$ 55.70  & 58.23 $\pm$ 13.51  & 49.84 $\pm$ 4.04   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset obtained using the ReliefFAttributeEval 
feature selection method (8 variables per book).}}
\label{tabla:results9}
\end{table*}

@@

\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  M5P     & 2.02 $\pm$ 0.01     & 205.52  & 556.90  & 36.64     & 40.37  \\
\hline
  LR      & 0.32 $\pm$ 0.00     & 261.04  & 547.42  & 46.54     & 39.68   \\
\hline
  SVM     & 81.74 $\pm$ 1.66    & 242.26  & 606.07   & 43.19    & 43.93   \\
\hline
  kNN     & 0.05 $\pm$ 0.00     & 216.05  & 506.34  & 38.52    & 36.70   \\
\hline
  MLP     & 47.80 $\pm$ 0.51    & 318.29 $\pm$ 43.96 & 587.50 $\pm$ 51.50  & 56.75 $\pm$ 7.84  & 42.59 $\pm$ 3.73   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset obtained using the CfsSubsetEval 
feature selection method (4 variables per book).}}
\label{tabla:results4}
\end{table*}

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=fig_time.eps,width=11cm}
\caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 8, 7 and 4 features each one). Plot shows that using categorical variables as part of the dataset makes the problem hard to solve. As expected, simpler methods are much faster to build the model than the complex ones.}}
\label{fig:time}
\end{center}
\end{figure}

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=fig_rae.eps,width=11cm}
\caption{\small{Relative absolute error (RAE $\%$) obtained after applying the five methods to the reduced datasets (16, 8, 7 and 4 features each one). The M5P model obtains the lowest errors, whatever the dataset used.}}
\label{fig:rae}
\end{center}
\end{figure}
